\documentclass{article}
\begin{document}
\newcommand{\myhalf}{\kern-0.125em{\thinspace\tiny\raisebox{0.5em}{1}\kern-0.125em\raisebox{0.25em}{/}\kern-0.25em\raisebox{-0.1em}{2}}}
\newcommand{\fracttb}[2]{\leavevmode\kern.1em
\raise.5ex\hbox{\scriptsize #1}\kern-.1em
\normalsize{/}\kern-.15em\lower.25ex\hbox{\scriptsize #2}}
  \begin{flushright}

{\LARGE NITIN NIZHAWAN}\\[11pt]
HNo. 47,\\
Guru Nanak/Tagore Marg,\\
Kewal Park, Azadpur,\\
Delhi - 110033\\
Mobile - (+91) 9971847784
  \end{flushright}
\hrulefill

\begin{flushleft} {\large\bf Objective}
\end{flushleft}
Seeking a position to make significant contribution to the field of computers and to the growth of company by utilizing and continuously enhancing my skills and abilities.
\begin{flushleft}
\large\bf{Experience}
\end{flushleft}

\begin{center}
   {\bf Adobe Systems India Pvt. Ltd.} (2011 -- present)\\
\end{center}
\begin{flushright} --- 3\fracttb{1}{2}  Years, Java, C{}\verb!++!, Scala, *nix \end{flushright}
   Worked in Adobe LiveCyle team on Document Service component. LiveCycle Document Services provides various APIs for customers to convert XFA documents into PDF, PS, PCL, ZPL and other printer formats.\\
   
   My role in team include working mostly in Java code interacting with native components using CORBA. Also some exposure to C{}\verb!++! for native components on both Windows as well as *nix system.
\begin{center}
   {\bf SuccessFactors India Pvt. Ltd.} (2010 -- 2011)\\ 
\end{center}
\begin{flushright}--- 6 Months, Javascript\end{flushright}
   I worked in Employee Central Team and my role involved developing UI components for a cloud based HR product.
\begin{center}
   {\bf Cisco Systems India Pvt. Ltd.} (2008 -- 2010)\\
\end{center}
\begin{flushright} --- 2\fracttb{1}{2} Years, Java, Struts \end{flushright}
   I worked in Cisco CallManager team. Working on Admin components. Work involved Java/Struts based web components hosted on Tomcat in a Redhat System.
\begin{flushleft}
\large\bf{Education}
\end{flushleft}
\begin{itemize}
\item M.E. Computer Science {\it\&} Applications.
\item  B.Tech. Mechanical {\it\&} Automation Engineering.
\item  12\textsuperscript{th} (C.B.S.E), Govt. Boys Senior Sec. School, Shakti Nagar No. 1 
\item  10\textsuperscript{th} (C.B.S.E), Govt. Boys Senior Sec. School, Model Town No. 1 
\end{itemize}
\begin{flushleft}
{\bf Personal Details}
\end{flushleft}
Father's Name : Naresh Kumar\\
Date of Birth : 30\textsuperscript{th} April, 1985
\vfill
\hrulefill
\end{document}
